Manuscript_Github_Pchabaudi_pir

### 2022-07-24 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_pirAnalysis.Rmd
Save ancestral pir expression plot

(
  p <- ggplot(data = cir_plot, 
              aes(x = time, 
                  y = sum_tpm,
                  fill = transmission)) +
    stat_summary(fun.y = median, fun.ymin = median, fun.ymax = median,
                 geom = "bar", width = 0.75, size = 0.25, position = 'dodge') +
    scale_y_continuous(breaks = y_scale) +
    geom_point(stat = 'identity', position = position_dodge(width = 0.75)) +
    ylab(as.expression(bquote('Total'~italic(.('PCHAS_0101200'))~'TPM'))) +
    xlab('Asexual blood stage development cycle') +
    theme_classic() +
    theme(axis.text.x=element_text(angle = 0, 
                                   vjust = 0.5,
                                   size = 13))
)

if(global_save_var){
  ggsave2(filename = 'Manuscript_ancestralPir_BarChart.pdf',
          plot = p,
          dpi = 300,
          width = 15,
          height = 10,
          units = 'cm')
}

>>>>

(
  p <- ggplot(data = cir_plot, 
              aes(x = time, 
                  y = sum_tpm,
                  fill = transmission)) +
    stat_summary(fun.y = median, fun.ymin = median, fun.ymax = median,
                 geom = "bar", width = 0.75, size = 0.25, position = 'dodge') +
    scale_y_continuous(breaks = y_scale) +
    scale_fill_manual(values = cbPalette) +
    geom_point(stat = 'identity', position = position_dodge(width = 0.75)) +
    ylab(as.expression(bquote('Total ancestral '~italic(.('pir'))~'TPM'))) +
    xlab('Asexual blood stage development cycle') +
    theme_classic() +
    theme(axis.text.x=element_text(angle = 0, 
                                   vjust = 0.5,
                                   size = 10))
)

if(global_save_var){
  ggsave(filename = 'plots/ancestralPir_BarChart.pdf',
          plot = p,
          dpi = 300,
          width = 15,
          height = 10,
          units = 'cm')
}
